Dish: Distribution-oblivious Shell Scripting

### 2019-11-23 pldi/draft.tex
Nits

This section reflects on \sys's design and implementation, touches on future work, and closes the paper.

@@

\sys does not adequately handle failures or network partitions in the general sense, which would include re-scheduling passes that were executing on failed replicas.
Prior work on fault-tolerant distributed stream processing can be of significant aid here.

@@

\heading{Conclusion}
This paper presented \sys, a shell variant that automatically and correctly scales out distribution-oblivious shell pipelines. 
\sys's insight is that shell pipelines already express stream computations that can be automatically distributed.
To achieve this, \sys
  decomposes primitives into distributability classes,
  identifies high-distributability stages,
  applies rewriting rules for largest possible subprograms,
  and orchestrates the execution of the distributed program.
% Its runtime component provides orchestration and planning support during the execution of the program.
Experiments with complex pipelines show substantial speedups and the ability to operate on large input datasets, all without any developer input.

>>>>

This section reflects on \sys's design and implementation, touches on future work, and concludes the paper.

@@

\sys does not adequately handle failures or network partitions in the general sense, which would require re-scheduling passes on failed replicas.
Prior work on fault-tolerant distributed stream processing can be of significant aid here.

@@

\heading{Conclusion}
This paper presented \sys, a shell variant that automatically and correctly scales out distribution-oblivious shell pipelines. 
\sys's insight is that shell pipelines already express streaming computations that can be automatically distributed.
To achieve its goal, \sys
  decomposes primitives into distributability classes,
  identifies high-distributability stages,
  applies rewriting rules for largest possible subprograms,
  and orchestrates the execution of the distributed program.
% Its runtime component provides orchestration and planning support during the execution of the program.
Experiments with complex pipelines show substantial speedups and the ability to operate on large input datasets, all without any developer input.
